Towards a miniKanren with fair search strategies

### 2019-06-27 Paper/paper.tex
clean up repo
(formal) proof --> proofs

@@

%\subsection{Compare \BFSimp{} with \BFSser{}}

%In this subsection,
Now we compare the pure subset of \BFSimp{} with \BFSser{}. We 
focus on the pure subset because \BFSser{} is designed for a pure 
relational programming system. We prove in Coq that these two search strategies 
are semantically equivalent, since the result of \texttt{(run n ? g)} is 
the same either way. (See supplements for the formal proof.) To 
compare efficiency, we translate \BFSser{}'s Haskell code into Racket (See 
supplements for the translated code). The translation is direct due to the 
similarity of the two relational programming systems. The translated code is 
longer than \BFSimp{}. And it runs slower in all benchmarks. Details about 
differences in efficiency are in \autoref{sec:quan}.

@@

In this section, we describe related research. 
\citet{yang2010adventures} points 
out that a disjunct complex would be `fair' if it were a full and balanced tree.
\citet{seres1999algebra} describe a breadth-first search 
strategy. We present another implementation. Our implementation is semantically 
equivalent to theirs. But, ours is shorter and performs better in comparison 
with a straightforward translation of their Haskell code.
\citet{rozplokhas2018improving} address the non-commutativity of conjunction, 
while our work about \disj{} fairness addresses the non-commutativity of 
disjunction.

@@

We analyze the definitions of fair \disj{} and fair \conj{}, then propose a 
new definition of fair \conj{}. Our definition of fair \conj{} is orthogonal 
with completeness.

We devise two new search strategies (i.e., balanced interleaving DFS 
(\DFSbi{}) and fair DFS (\DFSf{})) and devise a new 
implementation of \BFS{} (\BFSimp{}). These strategies have different features 
in fairness: \DFSbi{} has an almost-fair \disj{} and unfair \conj{}. 
\DFSf{} has fair \disj{} and unfair \conj{}. \BFS{} has both fair
\disj{} and fair \conj{}. No search strategy here combines unfair 
\disj{} and fair \conj{}. This is because we haven't seen a case where these 
kinds of search strategies would be interesting.

Our quantitative evaluation shows that \DFSbi{} is a competitive 
alternative to \DFSi{}, the current miniKanren search strategy,
and that \BFSimp{} is more practical than \BFSser{}.

>>>>

Source code of implementations, examples, benchmarks, and formal proofs are 
available at the 
following URL:

\begin{center}
\url{https://github.com/LuKC1024/Towards-a-miniKanren-with-fair-search-strategies}
\end{center}

@@

Now we compare the pure subset of \BFSimp{} with \BFSser{}. We 
focus on the pure subset because \BFSser{} is designed for a pure 
relational programming system. We prove in Coq that these two search strategies 
are semantically equivalent, since the result of \texttt{(run n ? g)} is 
the same either way. (See the GitHub repository for the formal proofs.) To 
compare efficiency, we translate \BFSser{}'s Haskell code into Racket. (See the 
GitHub repository for the translated code.)
The translation is direct due to the 
similarity of the two relational programming systems. The translated code is 
longer than \BFSimp{}. And it runs slower in all benchmarks. Details about 
differences in efficiency are in \autoref{sec:quan}.

@@

In this section, we describe related research. 
\citet{yang2010adventures} points 
out that a disjunct complex would be `fair' if it were a full and balanced tree.
\citet{seres1999algebra} describe BFS. We present another implementation. Our 
implementation is semantically 
equivalent to theirs. But, ours is shorter and performs better in comparison 
with a straightforward translation of their Haskell code.
\citet{rozplokhas2018improving} address the non-commutativity of conjunction, 
while our work about \disj{} fairness addresses the non-commutativity of 
disjunction.

@@

%We analyze the definitions of fair \disj{} and fair \conj{}, then propose a 
%new definition of fair \conj{}. Our definition of fair \conj{} is orthogonal 
%with completeness.

We analyze the definitions of fairness. Implementation of \disj{} can be fair, 
almost-fair, or unfair, depending on how evenly it allocates computational 
resources to spaces related to disjunctive goals. Implementation of \conj{}
can be fair or unfair, depending on how evenly it allocates computational 
resources to spaces related to states in the same bucket. Our definition of 
fair \conj{}, unlike the one by \citet{seres1999algebra}, is orthogonal with 
completeness.

%We devise two new search strategies (i.e., balanced interleaving DFS 
%(\DFSbi{}) and fair DFS (\DFSf{})) and devise a new 
%implementation of \BFS{} (\BFSimp{}). These strategies have different features 
%in fairness: \DFSbi{} has an almost-fair \disj{} and unfair \conj{}. 
%\DFSf{} has fair \disj{} and unfair \conj{}. \BFS{} has both fair
%\disj{} and fair \conj{}. No search strategy here combines unfair 
%\disj{} and fair \conj{}. This is because we haven't seen a case where these 
%kinds of search strategies would be interesting.

We devise two new search strategies (i.e., \DFSbi{} and \DFSf{}) and devise a 
new implementation of \BFS{}, \BFSimp{}. These strategies have different 
features in fairness: \DFSbi{} has an almost-fair \disj{} and unfair \conj{}. 
\DFSf{} has fair \disj{} and unfair \conj{}. \BFS{} has both fair
\disj{} and fair \conj{}. No search strategy here combines unfair 
\disj{} and fair \conj{}. This is because we haven't seen a case where these 
kinds of search strategies would be interesting.

Our quantitative evaluation shows that \DFSbi{} and \DFSf{} are competitive 
alternatives to \DFSi{}, the current miniKanren search strategy, and that 
\BFSimp{} is more practical than \BFSser{}.
